---
title: "Investing in New Sector:Biogas"
author: "Tani"
date: "2024-07-22"
output: html_document
bibliography: citation.bib
csl: acta-naturae.csl
---
Using decisionSupport to generate probabilistic simulations of  investing in New Sector: Biogas in a farm-size household @adeoti_engineering_2000.
We use the decisonSupport() function to perform probabilistic Monte Carlo simulations. The function performs calculations using distributions and ranges which is a major advantage over traditional spreadsheet calculations. In a Monte Carlo simulation, a particular calculation is repeated many times. Each time, a random draw from defined distribution of each variable are used as inputs for calculating the function. The output then consists of a set of values instead of single estimates. @luedeling_decisionsupport_2022-1.

The function requires two arguments:

1. A data table (.csv format) specifying the names and distributions for all uncertain variables and,

2. An R function that predicts decision outcomes based on the variables named in the data table.

The chance_event() function calculates the time series occurrence of particular events. This function requires two main arguments:

1. The probability that a  household will invest in a given year and

2. The time line for the simulation.

The value varier function vv() produces realistic time series of data that includes year-to-year variation around a specified mean. This is determined by a desired coefficient of variation. Both mean and coefficient of variation are provided to the model via the input table.

The discount() function calculated NPV in the last step of the decision modeling procedure. The function implements discounting of future costs or benefits by a decision maker-specific discount rate, which is also specified in the input tables.

The cost-benefit model AF_benefit calculates the NPV:

```{r }
library(decisionSupport)
input_estimates <- read.csv("input_estimates.csv")

make_variables <- function(est,n=1)
{ x<-random(rho=est, n=n)
for(i in colnames(x)) assign(i,
                             as.numeric(x[1,i]),envir=.GlobalEnv)
}

make_variables(as.estimate(input_estimates))
```

```{r}

# Define the decision function
decision_function <- function(x, varnames){
  #the baseline is just a normal income without bio gas
  annual_household_income <- income_per_month * 12 
  
  # calculate the cost 
  
  # establishment cost, to be paid only for th first year
  biogas_establishment_cost <- installation_cost
  
  # annual cost
  # with manure as raw material
  biogas_manure_cost_precalc <- biogas_cost_per_year + 	
    labour_cost + equipement_cost + manure_raw_material_cost
  biogas_manure_cost <- vv(biogas_manure_cost_precalc,var_CV, n_years)
  # add the annual cost with establishment cost for the first year
  biogas_manure_cost[1] <- biogas_manure_cost[1] + biogas_establishment_cost
  
  # with raw material from industrial based (?)
  biogas_industry_cost_precalc <- biogas_cost_per_year + 	
    labour_cost + equipement_cost + industry_raw_material_cost
  biogas_industry_cost <- vv(biogas_industry_cost_precalc,var_CV, n_years)
  # add the annual cost with establishment cost for the first year
  biogas_industry_cost[1] <- biogas_industry_cost[1] + biogas_establishment_cost
  
  
  # Profit from biogas production system
  # how much bigas we can produced per year
  #we can assume that the machine will be running 15 per month
  biogas_product_per_year_precalc <- biogas_product * 15 * 12
  biogas_product_per_year <- vv(biogas_product_per_year_precalc,var_CV, n_years)
  
  # revenue of biogas
  # to get the net revenue subtract the annual operation cost from the price
   annual_revenue_biogas_from_manure <- biogas_product_per_year - biogas_price
  
manure_biogas_result <- annual_revenue_biogas_from_manure - biogas_manure_cost
household_income_with_biogas_manure <- manure_biogas_result + annual_household_income

industry_biogas_result <- annual_revenue_biogas_from_manure - biogas_industry_cost
household_income_with_biogas_industry <- industry_biogas_result + annual_household_income

# calculate NPV

NPV_household_income_with_biogas_manure <-
  discount(household_income_with_biogas_manure, discount_rate, calculate_NPV = TRUE)

NPV_household_income_with_biogas_industry <-
  discount(household_income_with_biogas_industry, discount_rate, calculate_NPV = TRUE)

NPV_household <- discount(annual_household_income, discount_rate, calculate_NPV = TRUE)

 
return(list(manure_based_biogas_NPV = NPV_household_income_with_biogas_manure,
            industry_based_biogas_NPV = NPV_household_income_with_biogas_industry,
            NO_biogas_NPV = NPV_household,
            NPV_decision_do = NPV_household_income_with_biogas_manure - NPV_household,
            Cashflow_decision_do = manure_biogas_result))
}

```

The probabilistic simulation was implemented using the decisionSupport function to return a Monte Carlo data table with 1, 000 values for each of the input and response variables in the return list. A VIP score generated for each input variable of the PLS regression indicate its influenctial importance contriduting to model outcome.
```{r }
mcSimulation_results <- decisionSupport::mcSimulation(
  estimate = decisionSupport::estimate_read_csv("input_estimates.csv"),
  model_function = decision_function,
  numberOfModelRuns = 1e3, #run 1,000 times
  functionSyntax = "plainNames"
)

# Plot Net Present Value (NPV) distributions 
decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_results, 
                                    vars = c("NPV_decision_do", 
                                             "NO_biogas_NPV","industry_based_biogas_NPV", "manure_based_biogas_NPV"),
                                    method = 'smooth_simple_overlay', 
                                    base_size = 7)

decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_results, 
                                    vars = c("NPV_decision_do",
                                             "NO_biogas_NPV","industry_based_biogas_NPV", "manure_based_biogas_NPV"),
                                    method = 'boxplot')




```


```{r}
## Cashflow analysis

plot_cashflow(mcSimulation_object = mcSimulation_results, cashflow_var_name = "Cashflow_decision_do")

#### Projection to Latent Structures (PLS) analysis

pls_result <- plsr.mcSimulation(object = mcSimulation_results,
                                resultName = names(mcSimulation_results$y)[3], ncomp = 1)

plot_pls(pls_result, threshold = 0)



```

The outcome table is then used to calculate the Value of Information for uncertain variables using the multi_EVPI function in the decisionSupport package 

The multi_EVPI() function calculates the expected value of perfect information (EVPI) for multiple variables in the model using the simulation outcome table from the decisionSupport()function.

```{r}
# Value of Information (VoI) analysis
mcSimulation_table <- data.frame(mcSimulation_results$x, mcSimulation_results$y[1:4])
#
evpi <- multi_EVPI(mc = mcSimulation_table, first_out_var = "manure_based_biogas_NPV") # first value on return result
plot_evpi(evpi, decision_vars = "NPV_decision_do")
# too high uncertain for the equipement.. so in order to get a PI you should
#spend not more than 50,000

```


```{r}
compound_figure(mcSimulation_object = mcSimulation_results, input_table = input_estimates, 
                plsrResults = pls_result, EVPIresults = evpi, 
                decision_var_name = "NPV_decision_do", 
                cashflow_var_name = "Cashflow_decision_do", base_size = 7)



```



## References



